---
title: "The acceptability of two reflexives in one clause: identity, blocking and dialectual variations"
author: "Chaoyi Chen"
institute: "Rutgers University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["hygge", "rutgers", "rutgers-fonts",]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

# Background

* Chinese has two kinds of reflexives: the simple reflexive *ziji* 'self' and the complex reflexive *ta-ziji* 'him-self'.

* When in a subordinate clause, both *ziji* and *ta-ziji* can refer to the subject in the main clause.

  * *John* thinks that *ziji*/*ta-ziji* is clever.
  
* I am curious about the case where two reflxives appears in subordinate clause.  

  * *John* thinks that REF1 (*ziji* or *ta-ziji*) cheats REF2 (*ziji* or *ta-ziji*).

* In particular, I wonder what affect the acceptability of this case. Three factors are considered: 

  * whether or not two reflexives are identical 
  * whether or not a less specific reflexive precedes a more-specific reflexive (*ziji*-*taziji* vs. other three types; "blocking"hereafter)
  * dialectual background (northern Chinese speakers and Southern Chinese speakers); 




---


# The methods


* This is a hypothetical project.

* **Participant:** 100; 50 northern Chinese speakers and 50 southern Chinese speakers

* **Procedure** Participants completed the tests individually and finished the following tasks in order: a consent form (5 mins), a language background questionnaire (5 mins), an acceptability rating task (30 mins).

* **Materials** 4 test sentences in total (one sentences for each type)  


* **The task** Participants will judge the acceptability of 20 sentences: 8 practice sentences and 12 non-practice sentences (8 fillers, 4 experimental). Sentence items were presented one at a time which participants rated on a scale from 1 (very bad) to 7 (very good).



---

# The results

* Three categorical independent variables; one ordered dependent variable (a 7-point Likert scale).

* This study used Cumulative Link Mixed Models (or CLMMs), which will test both three fixed effects and random effects.

* Cumulative Link Mixed Models is for the data with the defendant variable as oridinal.
---
# The results--data frame

```{r, 'df', echo=F,warnings=F, message=F}
df_tidy<- read.csv("~/Desktop/finalds4ling/Data_tidy_raw/data_tidy1.csv")
head(df_tidy)
```
---
# The results--Blocking
.pull-left[
```{r, 'plot11', echo=F,warnings=F, message=F}
library("tidyverse")
df_tidy %>%
  ggplot(., aes(x = Blocking, y= rating)) + # set up varibles 
  geom_boxplot() # make a plot
```
]
.pull-right[
```{r, 'plot12', echo=F,warnings=F, message=F}
df_tidy %>%
   group_by(Blocking) %>%
   summarise(mean_rating = mean(rating))
```
]
---

# The results--Identity
.pull-left[
```{r, 'plot21', echo=F,warnings=F, message=F}
library("tidyverse")
df_tidy %>%
  ggplot(., aes(x = Identity, y= rating)) + # set up varibles 
  geom_boxplot() # make a plot
```
]
.pull-right[
```{r, 'plot22', echo=F,warnings=F, message=F}
df_tidy %>%
   group_by(Identity) %>%
   summarise(mean_rating = mean(rating))
```
]
---
# The results--Dialectual background
.pull-left[
```{r, 'plot31', echo=F,warnings=F, message=F}
library("tidyverse")
df_tidy %>%
  ggplot(., aes(x = dia, y= rating)) + # set up varibles 
  geom_boxplot() # make a plot
```
]
.pull-right[
```{r, 'plot32', echo=F,warnings=F, message=F}
df_tidy %>%
   group_by(dia) %>%
   summarise(mean_rating = mean(rating))
```
]

---
# The results--ordered regression models


```{r, 'regression', echo=T,warnings=F, message=F}
library("ordinal")
fm1 <- clm(as.factor(rating) ~ 1, data = df_tidy)
fm2 <- clm(as.factor(rating) ~ Blocking, data = df_tidy)
fm3 <- clm(as.factor(rating) ~ Blocking + Identity , data = df_tidy)
fm4 <- clm(as.factor(rating) ~ Blocking + Identity + dia, data = df_tidy)
fm5 <- clmm(as.factor(rating) ~ Blocking + Identity + dia + (1|id), data = df_tidy)
anova(fm1,fm2,fm3,fm4,fm5)
```
---


# Conclusion

  * The sentences with identical reflexives have higher score than the sentences with different reflexives.

  * The acceptability rating of the sentences in question is lower in Northern speakers than in Northern speakers.
  * The acceptability rating of the sentences in question is lower for Northern speakers than  southern speakers.

* The random effect does not have a main effect in this study.

* If we have ordinal dependent variable, the assumption diagnostics still work?



